HO unification from object language to meta language

### 2024-02-26 paper/main.tex
typos in tex

Our encoding of DTT may look ``semi shallow'' since we we use the meta language
lambda abstraction but not its application (for the terms of type \elpiIn{tm}).
A fully shallow encoding unfortunately does not fit our use case, although
it would make the running example work:

>>>>

Our encoding of DTT may look ``semi shallow'' since we use the meta-language
lambda abstraction but not its application (for the terms of type \elpiIn{tm}).
A fully shallow encoding unfortunately does not fit our use case, although
it would make the running example work:
